---
title: "R Notebook"
output: html_notebook
---

Movies Project
set the current working directory
```{r}
setwd("C:/Users/nithi/Downloads/Movies-Project")
```
Import the required libraries
```{r}
library(dplyr)
library(ggplot2)
library(plotly)
library(tidyr)
library(rjson)
library(jsonlite)
library(purrr)
library(gdata)
library(stringr)
library(tidyverse)
library(magrittr)
library(shiny)
library(dummies)
library(data.table)
library(lubridate)


```

Loading the movies and credits data
```{r}
movies <- read.csv(file = "data/movies_metadata.csv", stringsAsFactors = FALSE)
credits <- read.csv(file = "data/credits.csv", stringsAsFactors = FALSE)
```

Loading the keywords and ratings data
```{r}
keywords <- read.csv(file = "data/keywords.csv", stringsAsFactors = FALSE)
ratings <- read.csv(file = "data/ratings.csv", stringsAsFactors = FALSE)
```



Looking at the movies data
```{r}
t(head(movies,1))
```
Summary of movies data
```{r}
summary(movies)
```


Looking at the credits data
```{r}
head(credits)
```

Summary of credits data
```{r}
summary(credits)
```


Looking at the keywords data
```{r}
t(head(keywords,1))
```
Summary of movies data
```{r}
summary(keywords)
```

Looking at the ratings data
```{r}
t(head(ratings,1))
```
Summary of movies data
```{r}
summary(ratings)
```



Looking for na values in each column of movies data
```{r}
lapply(movies,function(x){length(which(is.na(x)))})
```
Looking for na values in each column of movies data
```{r}
lapply(credits,function(x){length(which(is.na(x)))})
```

Looking for na values in each column of keywords data
```{r}
lapply(keywords,function(x){length(which(is.na(x)))})
```

Looking for na values in each column of ratings data
```{r}
lapply(ratings,function(x){length(which(is.na(x)))})
```

Checking the dimension of movies
```{r}
dim(movies)
```

Checking the dimension of credits
```{r}
dim(credits)
```

Checking the dimension of keywords
```{r}
dim(keywords)
```

Checking the dimension of ratings
```{r}
dim(ratings)
```



Since, we have considerably less na values, removing na's from the movies data.
```{r}
movies <- na.omit(movies)
```
checking whether the na values are removed
```{r}
lapply(movies,function(x){length(which(is.na(x)))})
```

```{r}
movies$year <-format(as.Date(movies$release_date, format="%m/%d/%Y"),"%Y")
```


```{r}
movies = movies[!duplicated(movies$id),]
```

```{r}
dim(movies)
```


Scaling the movies budget to millions and converting the type of the budget.
```{r}
movies$budget <- as.numeric(movies$budget)
dim(is.null(movies$budget))
movies$budget <-round(as.numeric(movies$budget)/1000000, 2)
```

Scaling the movies revenue to millions and converting the type of the revenue.
```{r}
movies$revenue <- as.numeric(movies$revenue)
dim(is.null(movies$revenue))
movies$revenue <-round(as.numeric(movies$revenue)/1000000, 2)
```

```{r}
dim(movies)
```


```{r}
credits <- subset(credits, credits$cast != "[]")
```

Parsing the cast data
```{r}
cast_text <- sub("\\%\\$\\%", "", gsub("\'|\"|\\[|\\]|\\{|\\}|,", "", gsub("\'cast_id\':|\'character\':|\'credit_id\':|\'gender\':|\'id\':|\'name\':|\'order\':|\'profile_path\':", "%$%", credits$cast)))
  
s<- strsplit(cast_text, "\\%\\$\\%")



cast_data<- data.frame(movies_id = rep(credits$id, sapply(s, length)/8), matrix(trimws(unlist(s)), ncol=8, byrow = TRUE), stringsAsFactors = FALSE)

#cast_data <- data.frame(matrix(trimws(cbind(credits$id, unlist(strsplit(cast_text, "\\%\\$\\%"),ncol = 8, byrow = TRUE)))), stringsAsFactors = FALSE)
  
names(cast_data) <- c("movies_id","cast_id", "character_name", "credit_id", "gender", "id", "name", "order", "profile_path")

#cast_data$order <- as.numeric(cast_data$order)

#cast_data <- cast_data[cast_data$order ==0,]

#cast_data$order <- as.numeric(cast_data$order)
#cast_data$gender <- as.numeric(cast_data$gender)
#cast_data$name <- as.character(cast_data$name)
#cast_data <- cast_data[c('name','order','gender')]
#cast_data <- subset(cast_data, cast_data$order == c(0,1))
```

```{r}
dim(cast_data)
```


```{r}
head(cast_data)
```


Removing special characters from the cast data
```{r}
cast_data <- as.data.frame(gsub("[[:punct:]]", "", as.matrix(cast_data))) 
```

Popular actors who acted on highest number of movies
```{r}
cast_data %>% count(name,id, sort = TRUE)
```

```{r}
cast_data %>% select(movies_id, name, character_name, order)
```

```{r}
movies_actors_data <- cast_data %>%
    left_join(movies %>% select(id, title, release_date, budget),
              by=c("movies_id" = "id"))  %>%
    group_by(id) %>%
    summarise(num_movies=n(),
              name=name[1],
              debut_character=character_name[1],
              debut_date=min(release_date),
              debut_movie=title[1],
              release_date = release_date[1],
              budget = budget[1]) %>%
    filter(budget > 0)

```

```{r}
movies_actors_data <- na.omit(movies_actors_data)
```

```{r}
dim(movies_actors_data)
```

```{r}
head(movies_actors_data)
```

```{r}
movies_actors_data$release_date <- as.Date(movies_actors_data$release_date, format="%m/%d/%Y")
movies_actors_data$debut_date <- as.Date(movies_actors_data$debut_date, format="%m/%d/%Y")
```


```{r}

movies_actors_data$year_delta <-
    as.numeric(movies_actors_data$release_date - 
                 movies_actors_data$debut_date)/365
```


```{r}
head(movies_actors_data)
```

```{r}
movies_actors_data = subset(movies_actors_data, movies_actors_data$year_delta != 0.000)
```

```{r}
dim(movies_actors_data)
```

```{r}
movies_actors_data$id <- as.numeric(movies_actors_data$id)
movies_actors_data$name <- as.character(movies_actors_data$name)
movies_actors_data$debut_character <- as.character(movies_actors_data$debut_character)
```

```{r}
movies_actors_data$release_date <-format(as.Date(movies_actors_data$release_date, format="%m/%d/%Y"),"%Y")
```

```{r}
movies_actors_data$release_date <- as.numeric(movies_actors_data$release_date)
```


```{r}
plot_by_actor <-  movies_actors_data %>%
    filter(num_movies > 3) %>%
    ggplot(aes(x=release_date, 
               y=budget, 
               group=id, colour=name,
               tt1=name, tt2=budget)) +
    geom_point(alpha=0.2) + 
    ylab("Budget of movie in million$") +
    xlab("Release Date") 
  
```


```{r}
ggplotly(plot_by_actor, tooltip =c("tt1", "tt2"))
```


Taking only the main actors into account from the cast data
```{r}
cast_data$order = as.factor(cast_data$order)
cast_data = cast_data[cast_data$order == 0,]
```

```{r}
head(cast_data)
```


```{r}
dim(cast_data)
```

Delete some columns that we dont need from cast data
```{r}
col_deleted_cast = c("cast_id", "character_name","id","profile_path", 'order', "credit_id", "gender" )
cast_data = cast_data[,!(names(cast_data) %in% col_deleted_cast)]
```

```{r}
dim(cast_data)
```

```{r}
head(cast_data)
```



Parsing the crew data
```{r}

crew_text <- sub("\\%\\$\\%", "", gsub("\'|\"|\\[|\\]|\\{|\\}|,", "", gsub("\'credit_id\':|\'department\':|\'gender\':|\'id\':|\'job\':|\'name\':|\'profile_path\':", "%$%", credits$crew)))

s<- strsplit(crew_text, "\\%\\$\\%")

crew_data<- data.frame(movies_id = rep(credits$id, sapply(s, length)/7), matrix(trimws(unlist(s)), ncol=7, byrow = TRUE), stringsAsFactors = FALSE)


#crew_data <- data.frame(matrix(trimws(unlist(strsplit(cast_text, "\\%\\$\\%"))), 
 #   ncol = 8, byrow = TRUE), stringsAsFactors = FALSE)

names(crew_data) <- c("movies_id","credit_id", "department", "gender", "id", "job", "name", "profile_path")


```

```{r}
dim(crew_data)
```

```{r}
head(crew_data)
```
Removing special characters from the crew data
```{r}
crew_data <- as.data.frame(gsub("[[:punct:]]", "", as.matrix(crew_data)))
```

popular crew members who worked on highest number of movies
```{r}
crew_data %>% count(name,id,sort=TRUE)
```

Taking only the directors into account from the crew data
```{r}
crew_data$job = as.factor(crew_data$job)
crew_data = crew_data[crew_data$job == "Director",]
```

```{r}
dim(crew_data)
```



Delete some columns that we dont need from crew data
```{r}
col_deleted_crew = c("credit_id", "department","gender","id", "job", "profile_path" )
crew_data = crew_data[,!(names(crew_data) %in% col_deleted_crew)]
```

```{r}
dim(crew_data)
```

```{r}
head(crew_data)
```

Aggregating different directors based on the movies
```{r}
crew_data$name <- as.character(crew_data$name)
crew_data = aggregate(.~crew_data$movies_id,crew_data , paste, collapse=",")
```

```{r}
head(crew_data)
```

```{r}
col_deleted_crew = c("movies_id" )
crew_data = crew_data[,!(names(crew_data) %in% col_deleted_crew)]
```

```{r}
names(crew_data) <- c("movies_id","name")
```

```{r}
head(crew_data)
```

```{r}
dim(crew_data)
```

Having a look at keywords from keywords data
```{r}
head(keywords$keywords)
```

Splitting keywords data into separate columns
```{r}

keywords_text <- sub("\\%\\$\\%", "", gsub("\'|\"|\\[|\\]|\\{|\\}|,", "", gsub("\'id\':|\'name\':", "%$%", keywords$keywords)))

s<- strsplit(keywords_text, "\\%\\$\\%")

keywords_data<- data.frame(keywords_id = rep(keywords$id, sapply(s, length)/2), matrix(trimws(unlist(s)), ncol=2, byrow = TRUE), stringsAsFactors = FALSE)


#crew_data <- data.frame(matrix(trimws(unlist(strsplit(cast_text, "\\%\\$\\%"))), 
 #   ncol = 8, byrow = TRUE), stringsAsFactors = FALSE)

names(keywords_data) <- c("movies_id","id", "name")


```

```{r}
dim(keywords_data)
```

```{r}
head(keywords_data)
```

```{r}
keywords_data %>% count(name,sort=TRUE)

```

```{r}
keywords.count = as.data.frame(table(keywords_data$name))
keywords.count[with(keywords.count, order(-Freq)),]
keywords.count = keywords.count[keywords.count$Freq > 500,]
keywords.count.names = as.character(keywords.count$Var1)
keywords.pattern = paste(keywords.count.names, collapse = '|')

```

```{r}
head(keywords.pattern)
```


```{r}
keywords_data_co = keywords_data %>% group_by(movies_id) %>% summarize(type = c("woman director","independent film","murder","based on novel","musical"), collapse = ',')

```

```{r}
keywords_data_co$new = lapply(keywords_data_co$type, FUN = function(x) { as.list(strsplit(x,", ")[[1]])})
```


```{r}
head(keywords_data_co)
```

```{r}
keywords_data_co = keywords_data_co[grep(keywords.pattern, keywords_data_co$new),]

```


```{r}
for(i in 1:nrow(keywords_data_co))
  {
  keywords_data_co[i,unlist(keywords_data_co[i, 'new'], use.names = F)] = 1
  }
```

One hot encoded data
```{r}
head(keywords_data_co)
```

```{r}
col_deleted_keywords =  c("type","new","collapse")

keywords_data_co = keywords_data_co[, !(names(keywords_data_co) %in% col_deleted_keywords)]
```

```{r}
keywords_data_co[is.na(keywords_data_co)] = 0
```

```{r}
head(keywords_data_co)
```

Having a look at movie genres from movies data
```{r}
head(movies$genres)
```

Splitting genre data into separate columns
```{r}

genres_text <- sub("\\%\\$\\%", "", gsub("\'|\"|\\[|\\]|\\{|\\}|,", "", gsub("\'id\':|\'name\':", "%$%", movies$genres)))

s<- strsplit(genres_text, "\\%\\$\\%")

genres_data<- data.frame(movies_id = rep(movies$id, sapply(s, length)/2), matrix(trimws(unlist(s)), ncol=2, byrow = TRUE), stringsAsFactors = FALSE)


#crew_data <- data.frame(matrix(trimws(unlist(strsplit(cast_text, "\\%\\$\\%"))), 
 #   ncol = 8, byrow = TRUE), stringsAsFactors = FALSE)

names(genres_data) <- c("movies_id","id", "name")


```

```{r}
dim(genres_data)
```

```{r}
head(genres_data)
```

We have 20 unique factors on genre data
```{r}
genres_plot <- genres_data %>% count(name,sort=TRUE)
```

```{r}
hist(genres_plot$name)
```


```{r}
genres.count = as.data.frame(table(genres_data$name))
genres.count[with(genres.count, order(-Freq)),]
genres.count = genres.count[genres.count$Freq > 1000,]
genre.count.names = as.character(genres.count$Var1)
count.pattern = paste(genre.count.names, collapse = '|')

```


```{r}
col_deleted_genres =  c("id")

genres_data = genres_data[, !(names(genres_data) %in% col_deleted_genres)]
```

```{r}
head(genres_data)
```


```{r}
genres_data_co = genres_data %>% group_by(movies_id) %>% summarize(type = paste(sort(unique(name)), collapse = ', '))

```

```{r}
genres_data_co$new = lapply(genres_data_co$type, FUN = function(x) { as.list(strsplit(x,", ")[[1]])})
```


```{r}
head(genres_data_co)
```

```{r}
genres_data_co = genres_data_co[grep(count.pattern, genres_data_co$new),]

```


```{r}
for(i in 1:nrow(genres_data_co)){
  genres_data_co[i,unlist(genres_data_co[i, 'new'], use.names = F)] = 1
}

```

One hot encoded data
```{r}
head(genres_data_co)
```

```{r}
col_deleted_genres =  c("type","new")

genres_data_co = genres_data_co[, !(names(genres_data_co) %in% col_deleted_genres)]
```

```{r}
genres_data_co[is.na(genres_data_co)] = 0
```

```{r}
head(genres_data_co)
```


Having a look at movie production companies from movies data
```{r}
head(movies$production_companies)
```

splitting production companies data into separate columns
```{r}
production_companies_text <-  sub("\\%\\$\\%", "", gsub("\'|\"|\\[|\\]|\\{|\\}|,", "", gsub("\'name\':|\'id\':", "%$%", movies$production_companies)))

s<- strsplit(production_companies_text, "\\%\\$\\%")

production_companies_data<- data.frame(movies_id = rep(movies$id, sapply(s, length)/2), matrix(trimws(unlist(s)), ncol=2, byrow = TRUE), stringsAsFactors = FALSE)

names(production_companies_data) <- c("movies_id","name", "id")

```

```{r}
dim(production_companies_data)
```

```{r}
head(production_companies_data)
```

Aggregating different production companies of movies
```{r}
production_companies_data = aggregate(.~production_companies_data$movies_id,production_companies_data , paste, collapse=",")
```

```{r}
head(production_companies_data)
```

```{r}
col_deleted_pc = c("movies_id","id" )
production_companies_data = production_companies_data[,!(names(production_companies_data) %in% col_deleted_pc)]
```

```{r}
names(production_companies_data) <- c("movies_id","name")
```

```{r}
head(production_companies_data)
```

```{r}
dim(production_companies_data)
```


Having a look at movie production countries from movies data
```{r}
head(movies$production_countries)
```

splitting production countries data into separate columns
```{r}
production_countries_text <-  sub("\\%\\$\\%", "", gsub("\'|\"|\\[|\\]|\\{|\\}|,", "", gsub("\'iso_3166_1\':|\'name\':", "%$%", movies$production_countries)))

s<- strsplit(production_countries_text, "\\%\\$\\%")

production_countries_data<- data.frame(movies_id = rep(movies$id, sapply(s, length)/2), matrix(trimws(unlist(s)), ncol=2, byrow = TRUE), stringsAsFactors = FALSE)

names(production_countries_data) <- c("movies_id","id", "name")

```

```{r}
dim(production_countries_data)
```

```{r}
head(production_countries_data)
```

Aggregating different production countries of movies
```{r}
production_countries_data = aggregate(.~production_countries_data$movies_id,production_countries_data , paste, collapse=",")
```

```{r}
head(production_countries_data)
```

```{r}
col_deleted_pct = c("movies_id","name" )
production_countries_data = production_countries_data[,!(names(production_countries_data) %in% col_deleted_pct)]
```

```{r}
names(production_countries_data) <- c("movies_id","name")
```

```{r}
head(production_countries_data)
```

```{r}
dim(production_countries_data)
```


Having a look at spoken languages of movies data
```{r}
head(movies$spoken_languages)
```


splitting languages data into seperate columns
```{r}
spoken_languages_text <-  sub("\\%\\$\\%", "", gsub("\'|\"|\\[|\\]|\\{|\\}|,", "", gsub("\'iso_639_1\':|\'name\':", "%$%", movies$spoken_languages)))

s<- strsplit(spoken_languages_text, "\\%\\$\\%")

spoken_languages_data <- data.frame(movies_id = rep(movies$id, sapply(s, length)/2), matrix(trimws(unlist(s)), ncol=2, byrow = TRUE), stringsAsFactors = FALSE)

names(spoken_languages_data) <- c("movies_id","id", "name")
```

```{r}
dim(spoken_languages_data)
```

```{r}
head(spoken_languages_data)
```


Aggregating different production countries of movies
```{r}
spoken_languages_data = aggregate(.~spoken_languages_data$movies_id,spoken_languages_data , paste, collapse=",")
```

```{r}
head(spoken_languages_data)
```

```{r}
col_deleted_sl = c("movies_id","name" )
spoken_languages_data = spoken_languages_data[,!(names(spoken_languages_data) %in% col_deleted_sl)]
```

```{r}
names(spoken_languages_data) <- c("movies_id","name")
```

```{r}
head(spoken_languages_data)
```

```{r}
dim(spoken_languages_data)
```

delete columns time stamp and user id from ratings data
```{r}
col_deleted_sl = c('userId', 'timestamp')
ratings = ratings[, !(names(ratings) %in% col_deleted_sl)]
```


Extracting mean values based on movie id's from ratings data
```{r}
ratings = aggregate(. ~ movieId, ratings, mean)
```

```{r}
head(ratings)
```

```{r}
dim(ratings)
```


```{r}
dim(movies)
```


```{r}
movies$belongs_to_collection = movies$belongs_to_collection != ''
movies[movies$belongs_to_collection, 'belongs_to_collection'] = 1
```

```{r}
movies$release_month <- month(as.IDate(movies$release_date, '%m/%d/%Y'))
```


Delete some columns that we dont need from movies
```{r}
col_deleted_movies =  c('homepage',"original_title","overview","poster_path","status","tagline","video", "genres", "production_companies", "production_countries","spoken_languages","adult","imdb_id","original_language")

movies = movies[, !(names(movies) %in% col_deleted_movies)]

```

view movies data
```{r}
head(movies)
```

```{r}
dim(movies)
```


Merging cast data to movies
```{r}
movies = merge(movies, cast_data, by.x = 'id', by.y = 'movies_id', all.x = TRUE)
```

```{r}
dim(movies)
```

```{r}
head(movies)
```

```{r}
names(movies) <- c("id","belongs_to_collection","budget","popularity","release_data","revenue","runtime","title","vote_average","vote_count","year","release_month","lead_actor")
```


Merging crew data to movies
```{r}
movies = merge(movies, crew_data, by.x = 'id', by.y = 'movies_id', all.x = TRUE)
```

```{r}
dim(movies)
```

Renaming the movies data
```{r}
names(movies) <- c("id","belongs_to_collection","budget","popularity","release_data","revenue","runtime","title","vote_average","vote_count","year","release_month","lead_actor","director")
```


```{r}
head(movies)
```

Merging keywords_data data to movies
```{r}
movies = merge(movies, keywords_data, by.x = 'id', by.y = 'movies_id', all.x = TRUE)
```

```{r}
dim(movies)
```

```{r}
head(movies)
```


Renaming the movies data
```{r}
names(movies) <- c("id","belongs_to_collection","budget","popularity","release_date","revenue","runtime","title","vote_average","vote_count","year","release_month","lead_actor","director","keywords")
```



Merging ratings data to movies
```{r}
ratings$movieId <- as.character(ratings$movieId)
```

```{r}
movies = merge(movies, ratings, by.x = 'id', by.y = 'movieId', all.x = TRUE)
```

```{r}
dim(movies)
```

```{r}
head(movies)
```

Renaming the movies data
```{r}
names(movies) <- c("id","belongs_to_collection","budget","popularity","release_date","revenue","runtime","title","vote_average","vote_count","year","release_month","lead_actor","director","keywords","rating")
```

Merging genres_data to movies
```{r}
movies = merge(movies, genres_data, by.x = 'id', by.y = 'movies_id', all.x = TRUE)
```

```{r}
dim(movies)
```

```{r}
head(movies)
```

Renaming the movies data
```{r}
names(movies) <- c("id","belongs_to_collection","budget","popularity","release_date","revenue","runtime","title","vote_average","vote_count","year","release_month","lead_actor","director","keywords","rating","genres")
```

Merging production_companies data to movies
```{r}
movies = merge(movies, production_companies_data, by.x = 'id', by.y = 'movies_id', all.x = TRUE)
```

```{r}
dim(movies)
```

```{r}
head(movies)
```

Renaming the movies data
```{r}
names(movies) <- c("id","belongs_to_collection","budget","popularity","release_date","revenue","runtime","title","vote_average","vote_count","year","release_month","lead_actor","director","keywords","rating","genres","production_company")
```

Merging production_countries_data data to movies
```{r}
movies = merge(movies, production_countries_data, by.x = 'id', by.y = 'movies_id', all.x = TRUE)
```

```{r}
dim(movies)
```

```{r}
head(movies)
```

Renaming the movies data
```{r}
names(movies) <- c("id","belongs_to_collection","budget","popularity","release_date","revenue","runtime","title","vote_average","vote_count","year","release_month","lead_actor","director","keywords","rating","genres","production_company","production_country")
```

Merging spoken_languages_data data to movies
```{r}
movies = merge(movies, spoken_languages_data, by.x = 'id', by.y = 'movies_id', all.x = TRUE)
```

```{r}
dim(movies)
```

```{r}
head(movies)
```

Renaming the movies data
```{r}
names(movies) <- c("id","belongs_to_collection","budget","popularity","release_date","revenue","runtime","title","vote_average","vote_count","year","release_month","lead_actor","director","keywords","rating","genres","production_company","production_country","spoken_language")
```

```{r}
head(movies)
```

```{r}
dim(movies)
```

```{r}
movies$lead_actor <- as.character(movies$lead_actor)
movies$lead_actor <- ifelse(is.na(movies$lead_actor), 'Unknown', movies$lead_actor)
```

```{r}
movies$director <- ifelse(is.na(movies$director), 'Unknown', movies$director)
```

```{r}
movies$keywords <- ifelse(is.na(movies$keywords), 'Unknown', movies$keywords)
```

```{r}
movies$production_company <- ifelse(is.na(movies$production_company), 'Unknown', movies$production_company)
```

```{r}
movies$production_country <- ifelse(is.na(movies$production_country), 'Unknown', movies$production_country)
```

```{r}
movies$spoken_language <- ifelse(is.na(movies$spoken_language), 'Unknown', movies$spoken_language)
```

```{r}
movies$release_date <- as.Date(movies$release_date, format="%m/%d/%Y")
```

```{r}
movies <- na.omit(movies)
```

```{r}
head(movies)
```

```{r}
dim(movies)
```


Delete budget and revenue from movies
```{r}
col_deleted_movies =  c("budget","revenue")

movies = movies[, !(names(movies) %in% col_deleted_movies)]

```

```{r}
head(movies)
```

```{r}
dim(movies)
```

Merging the one hot encoded data of movies and Genres

```{r}
head(genres_data_co)
```

```{r}
head(keywords_data_co)
```



```{r}
movies_and_genres = merge(movies, genres_data_co, by.x = 'id', by.y = 'movies_id', all.x = TRUE)
```

```{r}
head(movies_and_genres)
```


```{r}
dim(movies_and_genres)
```

```{r}
movies_and_genres[is.na(movies_and_genres)] = 0
```


Merging the one hot encoded data of movies and Keywords
```{r}
final_movies = merge(movies_and_genres, keywords_data_co, by.x = 'id', by.y = 'movies_id', all.x = TRUE)

```


```{r}
final_movies[is.na(final_movies)] = 0

```


```{r}
head(final_movies)
```


Delete budget and revenue from movies
```{r}
col_deleted_movies =  c("keywords","rating")

final_movies = final_movies[, !(names(final_movies) %in% col_deleted_movies)]

```



```{r}
dim(final_movies)
```


```{r}
names(final_movies) <- c("id","belongs_to_collection","popularity","release_date","runtime","title","vote_average","vote_count","year","release_month","lead_actor","director","rating","genres","production_company","production_country","spoken_language", "Comedy", "Crime", "Drama", "Science_Fiction","War","Romance","Horror","Thriller", "Action","Adventure","Fantasy", "Mystery", "Animation", "Family","Foreign","Documentary","Music","History","Western","TV_Movie","woman_director","independent_film","murder","based_on_novel","musical")

```


```{r}
head(final_movies)
```

```{r}
final_movies$production_company <- substr(final_movies$production_company,1,8)
```

```{r}
final_movies$director <- substr(final_movies$director,1,15)
```

```{r}
head(final_movies)
```

Stratified Random split on data
```{r}
library(caret)
```

```{r}
Only_for_fun <- final_movies
Only_for_fun$runtime[which(is.na(Only_for_fun$runtime))] <- mean(Only_for_fun$runtime,na.rm = TRUE)
Only_for_fun.null.count = lapply(Only_for_fun, function(x) { length(which(is.na(x))) })
```

```{r}
head(Only_for_fun)
```

```{r}
## 75% of the sample size
part <- floor(0.80 * nrow(Only_for_fun))

## set the seed to make your partition reproducible
set.seed(123)
train_ind <- sample(seq_len(nrow(Only_for_fun)), size = part)

Sample <- Only_for_fun[train_ind, ]
Vault <- Only_for_fun[-train_ind, ]

Sample$rating_class <- cut(Sample$rating, breaks=c(0,3,4,5), labels=c("L","A","U"))

```


```{r}
drop2 = c("rating","id","title","genres", "runtime")
Sample = Sample[, !(names(Sample) %in% drop2)]

```

```{r}
part2 <- floor(0.80 * nrow(Sample))
train_ind <- sample(seq_len(nrow(Sample)), size = part2)
Train <- Sample[train_ind, ]
Test <- Sample[-train_ind, ]

X <- Train[, !(names(Sample) %in% "rating_class")]
y <- Train$rating_class

Train.null.count = lapply(Train, function(x) { length(which(is.na(x))) })

```

repeated k-fold cross validation
```{r}
control <- trainControl(method='repeatedcv', 
                        number=10, 
                        repeats=3)
#Metric compare model is Accuracy
metric <- "Accuracy"
set.seed(123)
#Number randomly variable selected is mtry
mtry <- sqrt(ncol(X))
tunegrid <- expand.grid(.mtry=mtry)

rf_default <- train(rating_class~., 
                    data=Train, 
                    method='rf', 
                    metric='Accuracy', 
                    tuneGrid=tunegrid, 
                    trControl=control)

```

```{r}

memory.limit(size=5000000) 
```

```{r}
rf_default
```

```{r}

```

